Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-30 ms.qmd
Adding a bunch of new code to do climate analysis with interaction-based lnRRQ10 and also add these results and figures in. Updated supp figs as order changes

# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reductino in lnRRQ10
  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reuction in lnRRQ10
  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.

@@

Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95\% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95\% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`). While marine ectotherms had larger increases in variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95\% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95\% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B). Marine and freshwater habitats did not differ in the extent of variance increases at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95\% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95\% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`). There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B). Differences in variance between habitats were driven by different scaling relationships between mean and variance with slopes varying across habitat types (see *Supplementary Materials* scaling analyses, @tbl-slopes & @fig-mv).

@@

# Plot the effects with climate variation and predcitabiliy

  lnRRQ10_data_wild_acute_vs_acclim  %>% 
    ggplot(aes(x = acf_all, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Autocorrelation", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")

  lnRRQ10_data_wild_acute_vs_acclim  %>% 
    ggplot(aes(x = cv, y = lnRRQ10_ac_acclimate, color = habitat)) + geom_point() + facet_wrap(~habitat) + theme_classic() + my_theme() + labs(x = "Coefficient of Variation (CV)", y = "Acute - Acclimation", color = "Habitat") + geom_smooth(method = "lm", se = FALSE) + geom_smooth(method = "lm", se = FALSE, aes(group = habitat), linetype = "dashed") + theme(legend.position = "none")

  # Save model3_new
    saveRDS(model3_new, file = "./output/models/lnRRQ10_3_new")
    saveRDS(model3_new_bayes, file = "./output/models/lnRRQ10_3_new_bayes")

@@

col <- c("#0871B9", "#F3B40D", "#1BB908")
lnrrq10_temp <- ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
geom_point(aes(size = 1/sqrt(V), fill = habitat), alpha = 0.8, shape = 21, colour = "black") +
labs(x = TeX("Maximum Temperature ($^{\\circ}$C)"), y = TeX("$lnRR_{Q_{10}}"), size = "Precision (1/SE)", color = "Habitat") + 
ggplot2::geom_smooth(data = mod_table, 
ggplot2::aes(x = moderator , y = lowerPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = estimate), method = "loess", 
            formula = y ~ x, se = FALSE, colour = "black") + 
            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") +
theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))

@@

```{r, fig-accl_time}
#| label: fig-accl_time
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time for terrestrial (green), marine (orange) and freshwater (blue) habitats. Acclimation time is centered around the mean acclimation time (37.5 days) in the data. Not all studies reported acclimation time hence the total number of effects, *k*, was 1767. Raw effects are weighted by their precision (inverse sampling variance)."
  col <- c("#0871B9", "#F3B40D", "#1BB908")

  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)") + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))

@@

@@

@@

@@

 p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
  ggsave(p_mv, file = "./output/figures/figS6.png", height = 8, width = 8)

  p_mv <- magick::image_read("./output/figures/figS6.png")
  p_mv
```

@@

  ggsave(p3b, filename = "./output/figures/figS7.pdf", width = 11.5, height = 8)

  figs1 <- image_read("./output/figures/figS7.pdf")
  figs1
```

@@

############
# Full fig
############
figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait_vr, filename = "./output/figures/figS8.png", width = 28, height = 8, device = "png")

figbtrait <- magick::image_read("./output/figures/figS8.png")
figbtrait
```

@@

figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figcvr_lh, filename = "./output/figures/figS9.pdf", width = 28, height = 10, device = "pdf")

figcvr_lh <- magick::image_read("./output/figures/figS9.pdf")
figcvr_lh

@@

############
# Full fig
############
figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait, filename = "./output/figures/figS10.png", width = 28, height = 14, device = "png")

figbtrait <- magick::image_read("./output/figures/figS10.png")
figbtrait
```

@@

fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
ggsave(fig2, filename = "./output/figures/figS11.png", height = 20, width = 15)

img_fig2 <- magick::image_read("./output/figures/figS11.png")
img_fig2
```

@@

figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figvrtrait, filename = "./output/figures/figS12.png", height = 20, width = 15)

img_figvrtrait <- magick::image_read("./output/figures/figS12.png")
img_figvrtrait
```

@@

figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figcvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)

img_figcvrtrait <- magick::image_read("./output/figures/figS13.png")
img_figcvrtrait
```

@@

figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS14.png")

figS12 <- image_read("./output/figures/figS14.png")
figS12
```

@@

ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS15.pdf")

  p_acf <- image_read("./output/figures/figS15.pdf")
  p_acf 
```

@@

figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS16.png")

figs2 <- image_read("./output/figures/figS16.png")
figs2
```

@@

p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS17.png")

p_sim <- image_read("./output/figures/figS17.png")
p_sim
```

>>>>

# % change in mean acclimation relative to acute. Note that this is the change in two Q10 contrasts not the % difference between low and high temp (i.e., lnRR)
  # Calculate the mean lnRR for acclimation and acute, then calculate thir difference and make the relative change relative to acute to talk about % reduction in lnRRQ10 in relation to acute.
  change_f <- ((f_acclim - f_acute) / f_acute)*100; quantile(change_f, c(0.025, 0.975)) # 17% reduction in lnRRQ10
  change_m <- ((m_acclim - m_acute) / m_acute)*100; quantile(change_m, c(0.025, 0.975)) # 16% reduction in lnRRQ10
  change_t <- ((t_acclim - t_acute) / t_acute)*100; quantile(change_t, c(0.025, 0.975))
  avg_change <- (change_f + change_m + change_t) / 3; quantile(avg_change, c(0.025, 0.975)) # Could use weighted mean, but for now this seems fine.

@@

Physiological rate variance increased significantly more in freshwater compared to terrestrial ectotherms for acute responses ($\beta$ = `r mean(f_t_c_a)`, 95\% CI: `r quantile(f_t_c_a, 0.025)` to `r quantile(f_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_a))`), but not for acclimation responses because increases in rates were dampened by acclimation resulting in smaller increases in variance ($\beta$ = `r mean(f_t_c_aclim)`, 95\% CI: `r quantile(f_t_c_aclim, 0.025)` to `r quantile(f_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_t_c_aclim))`). While marine ectotherms had larger increases in variance compared to terrestrial ectotherms these were not significant (Acute: $\beta$ = `r mean(m_t_c_a)`, 95\% CI: `r quantile(m_t_c_a, 0.025)` to `r quantile(m_t_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_a))`; Acclimation: $\beta$ = `r mean(m_t_c_aclim)`, 95\% CI: `r quantile(m_t_c_aclim, 0.025)` to `r quantile(m_t_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(m_t_c_aclim))`)([@fig-2]B). Marine and freshwater habitats did not differ in the extent of variance increases at higher temperatures (Acute: $\beta$ = `r mean(f_m_c_a)`, 95\% CI: `r quantile(f_m_c_a, 0.025)` to `r quantile(f_m_c_a, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_a))`; Acclimation: $\beta$ = `r mean(f_m_c_aclim)`, 95\% CI: `r quantile(f_m_c_aclim, 0.025)` to `r quantile(f_m_c_aclim, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(f_m_c_aclim))`). There were no differences between $lnVR_{Q_{10_{acute}}}$ and $lnVR_{Q_{10_{acclimation}}}$ within any habitat ([@fig-2]B).

@@

@@

col <- c("#0871B9", "#F3B40D", "#1BB908")
lnrrq10_temp <- ggplot(data = lnRRQ10_data, aes(x = temp_2, y = effect_size)) + 
geom_point(aes(size = 1/sqrt(V), fill = habitat), alpha = 0.8, shape = 21, colour = "black") +
labs(x = TeX("Maximum Temperature ($^{\\circ}$C)"), y = TeX("$lnRR_{Q_{10}}"), size = "Precision (1/SE)", color = "Habitat") + 
ggplot2::geom_smooth(data = mod_table, 
ggplot2::aes(x = moderator , y = lowerPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", colour = "black") + 
ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, y = estimate), method = "loess", 
            formula = y ~ x, se = FALSE, colour = "black") + 
            scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col)+ labs(fill = "Habitat") + facet_wrap(~type)+
theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))

@@

```{r, fig-accl_time}
#| label: fig-accl_time
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and acclimation time for terrestrial (green), marine (orange) and freshwater (blue) habitats. Acclimation time is centered around the mean acclimation time (37.5 days) in the data. Not all studies reported acclimation time hence the total number of effects, *k*, was 1767. Raw effects are weighted by their precision (inverse sampling variance)."
  col <- rep(c("#0871B9", "#F3B40D", "#1BB908"), 2)

  accl_time <- bubble_plot(model1.2, mod = "c_accl_time", group = "spp", ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Centered Acclimaton Time (days)", at = list(type = c("acclim", "acute")), condition.nrow = 1, by = "type", k = FALSE) + geom_point(data = lnRRQ10_data, aes(x = c_accl_time, y = effect_size, fill = habitat), shape = 21, colour = "black") + scale_fill_manual(labels = c("f" = "Freshwater", "m" = "Marine", "t" = "Terrestrial"), values = col) + theme_classic() + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 24), 
                        legend.title = element_text(size = 26))

@@

  # Save model3_new
    saveRDS(model3_new, file = "./output/models/model3_new")
    saveRDS(model3_new_bayes, file = "./output/models/model3_new_bayes")

  } else{
        model3_new <- readRDS("./output/models/model3_new")
  model3_new_bayes <- readRDS("./output/models/model3_new_bayes")
}

#################################################
### Bayesian Slopes from model3_new_bayes
#################################################
 posteriors_model3_new_bayes <- posterior_samples(model3_new_bayes, "^b")

    slope_f_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"]
    slope_m_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"] + posteriors_model3_new_bayes[,"b_cv_c:habitatm"]
    slope_t_new_delta <- posteriors_model3_new_bayes[,"b_cv_c"] + posteriors_model3_new_bayes[,"b_cv_c:habitatt"]

##################################################
    # Models - Habitat subset
    # Used for making plots
##################################################
    # Subset data to habitat

    lnRRQ10_data_wild_acclim_t_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "t") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))
    lnRRQ10_data_wild_acclim_f_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "f") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))
    lnRRQ10_data_wild_acclim_m_delta <- lnRRQ10_data_wild_acute_vs_acclim %>% filter(habitat == "m") %>% filter(!is.na(cv_c)) %>% filter(!is.na(c_accl_time))

  # Check and prune tree

    # Terrestrial. 
        tree_lnrr_delta_wild_t <- tree_checks(data = lnRRQ10_data_wild_acclim_t_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
    tree_checks(data = lnRRQ10_data_wild_acclim_t_delta, tree = tree_lnrr_delta_wild_t, dataCol = "species_full", type = "check") # Good

  # Marine
    tree_lnrr_delta_wild_m <- tree_checks(data = lnRRQ10_data_wild_acclim_m_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
    tree_checks(data = lnRRQ10_data_wild_acclim_m_delta, tree = tree_lnrr_delta_wild_m, dataCol = "species_full", type = "check") # Good

  # Freshwater
    tree_lnrr_delta_wild_f <- tree_checks(data = lnRRQ10_data_wild_acclim_f_delta, tree = tree_p0.7, dataCol = "species_full", type = "prune")
    tree_checks(data = lnRRQ10_data_wild_acclim_f_delta, tree = tree_lnrr_delta_wild_f, dataCol = "species_full", type = "check") # Good

# Create the phylo correlation matrix
phylo_cor_wild_ac_acclim_t <- vcv(tree_lnrr_delta_wild_t, cor = TRUE)
phylo_cor_wild_ac_acclim_m <- vcv(tree_lnrr_delta_wild_m, cor = TRUE)
phylo_cor_wild_ac_acclim_f <- vcv(tree_lnrr_delta_wild_f, cor = TRUE)

  # Terrestrial Models: # Note that convergence issues with this model now given data drops too few for a random slope of max temp so need to drop from model. Removed max temp slope. Note some effects are not defined (missing SD for one group etc) so are dropped from model
    model_delta_t  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_ac_acclim_t), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_t_delta, control=list(iter.max=1000, rel.tol=1e-8))
    saveRDS(model_delta_t, "./output/models/model_delta_t")

    # Freshwater Models. Note some effects are not defined (missing SD for one group etc) so are dropped from model

    model_delta_f  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_ac_acclim_f), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f_delta)

    saveRDS(model_delta_f, "./output/models/model_delta_f")

    # Marine Models. Note some effects are not defined (missing SD for one group etc) so are dropped from model

    model_delta_m  <- metafor::rma.mv(lnRRQ10_ac_acclimate ~ max_temp_c + c_accl_time + cv_c, V = lnRRQ10_ac_acclimate_SV,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 + max_temp_c| spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_ac_acclim_m), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_m_delta)
    saveRDS(model_delta_m, "./output/models/model_delta_m")

  } else {
     model_delta_t <- readRDS("./output/models/model_delta_t")
     model_delta_f <- readRDS("./output/models/model_delta_f")
     model_delta_m <- readRDS("./output/models/model_delta_m")
}

@@

Like our analysis with $lnRR_{Q_{10_{acclimation}}}$, $\Delta lnRR_{Q_{10}}$ was also not related to climate variability that a given population experienced @fig-delta-climate.

@@

```{r, fig-delta-climate}
#| label: fig-delta-climate
#| fig-cap: "Past climate variability did not predict acclimation responses as measured by $\\Delta lnRR_{Q_{10}}$. Predicted mean acclimation (thick black line) $\\Delta lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) for wild populations across marine, freshwater and terrestrial habitats. Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals. Raw effects are weighted by their precision (inverse sampling variance). Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."

####################
# lnVR_Delta CV
####################
 dat_text <- data.frame(label = c(text(slope_f_new_delta), text(slope_m_new_delta), text(slope_t_new_delta)),
                       label2 = c(text(slope_f_new_delta, b = FALSE), text(slope_m_new_delta,b = FALSE), text(slope_t_new_delta,b = FALSE)),
                            p = c(p_text(slope_f_new_delta), p_text(slope_m_new_delta), p_text(slope_t_new_delta)),
                        title = c("Freshwater", "Marine", "Terrestrial"), 
                    condition = c("f", "m", "t"),
                            x = rep(0, 3),
                            y = rep(-1.1, 3))
y_adj = -3
size_axis =14

# Terrestrial
  p_t_rr <-  bubble_plot(model_delta_t, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,2)

# Marine
p_m_rr <-  bubble_plot(model_delta_m, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

# Freshwater
p_f_rr <-  bubble_plot(model_delta_f, mod = "cv_c", group = "spp", ylab = TeX("$\\Delta lnRR_{Q_{10}}$"), xlab = "Thermal Coefficient of Variation (CV)", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f_delta, aes(x = cv_c, y = lnRRQ10_ac_acclimate, size = 1/sqrt(lnRRQ10_ac_acclimate_SV)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

  p_cv_delta <- (p_t_rr + p_m_rr + p_f_rr) +
            plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))

  ggsave(p_cv_delta, width = 18, height = 10, filename = "./output/figures/figS6.png")

  p_cv_delta <- image_read("./output/figures/figS6.png")
  p_cv_delta

@@

 p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
  ggsave(p_mv, file = "./output/figures/figS7.png", height = 8, width = 8)

  p_mv <- magick::image_read("./output/figures/figS7.png")
  p_mv
```

@@

  ggsave(p3b, filename = "./output/figures/figS8.pdf", width = 11.5, height = 8)

  figs1 <- image_read("./output/figures/figS8.pdf")
  figs1
```

@@

############
# Full fig
############
figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait_vr, filename = "./output/figures/figS9.png", width = 28, height = 8, device = "png")

figbtrait <- magick::image_read("./output/figures/figS9.png")
figbtrait
```

@@

figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figcvr_lh, filename = "./output/figures/figS10.pdf", width = 28, height = 10, device = "pdf")

figcvr_lh <- magick::image_read("./output/figures/figS10.pdf")
figcvr_lh

@@

############
# Full fig
############
figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait, filename = "./output/figures/figS11.png", width = 28, height = 14, device = "png")

figbtrait <- magick::image_read("./output/figures/figS11.png")
figbtrait
```

@@

fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
ggsave(fig2, filename = "./output/figures/figS12.png", height = 20, width = 15)

img_fig2 <- magick::image_read("./output/figures/figS12.png")
img_fig2
```

@@

figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)

img_figvrtrait <- magick::image_read("./output/figures/figS13.png")
img_figvrtrait
```

@@

figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figcvrtrait, filename = "./output/figures/figS14.png", height = 20, width = 15)

img_figcvrtrait <- magick::image_read("./output/figures/figS14.png")
img_figcvrtrait
```

@@

figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS15.png")

figS12 <- image_read("./output/figures/figS15.png")
figS12
```

@@

ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS16.pdf")

  p_acf <- image_read("./output/figures/figS16.pdf")
  p_acf 
```

@@

figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS17.png")

figs2 <- image_read("./output/figures/figS17.png")
figs2
```

@@

p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS18.png")

p_sim <- image_read("./output/figures/figS18.png")
p_sim
```
